sWGS QC

### 2020-04-15 sWGS QC.Rmd
trying to re-process the qc dataset using the Barretts package

dir1 = '~/Data/BarrettsProgressionRisk/Analysis/pcf_perPatient/50kb/'
dir2 = '~/Data/BarrettsProgressionRisk/Analysis/validation/pcf_perPatient/50kb/'

@@

```{r, echo=F, fig.height=10}
res.variance = arrange(res.variance,varMAD_median)
cutoff = round(median(res.variance$varMAD_median)+sd(res.variance$varMAD_median)*2, 3)
#cutoff = 0.015

@@

```{r, echo=F}
val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
sheets = readxl::excel_sheets(val.file)[1:4]
all.val = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% dplyr::select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`, Cohort, Batch, RA, matches('Collection')) %>% 
    dplyr::filter(!is.na(`SLX-ID`) & RA == 'C.Kosmidou') %>% 
    mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) 
}))
all.val = all.val %>% dplyr::select(-Collection)

@@

all.val = all.val %>% rowwise %>% mutate_at(vars(`SLX-ID`), list(pastefun) ) %>% ungroup
all.val = all.val %>% mutate(
  `Hospital Research ID` = str_replace_all( str_remove_all(`Hospital Research ID`, " "), '/', '_'), 
  `Index Sequence` = str_replace_all(`Index Sequence`, 'tp', ''),
  Sample = paste(`SLX-ID`,`Index Sequence`,sep='.')
  )

>>>>

dir1 = '~/Data/BarrettsProgressionRisk/Analysis/pcf_perPatient/50kb/'
dir2 = '~/Data/BarrettsProgressionRisk/Analysis/qc_batches/pcf_perPatient/50kb/'

@@

```{r, echo=F, fig.height=10}
res.variance = arrange(res.variance,varMAD_median)
cutoff = median(res.variance$varMAD_median)+sd(res.variance$varMAD_median)*2
cutoff = 0.008

@@

```{r, echo=F}
val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/qc_batches/qc_batches.xlsx'
sheets = readxl::excel_sheets(val.file)
all.val = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% dplyr::select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`,  Batch, matches('Collection')) %>% 
    mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) 
})) %>% dplyr::select(-Collection)

@@

all.val = all.val %>% rowwise %>% mutate_at(vars(`SLX-ID`), list(pastefun) ) %>% ungroup
all.val = all.val %>% mutate(
  `Hospital Research ID` = str_replace_all( str_remove_all(`Hospital Research ID`, " "), '/', '_'), 
  `Index Sequence` = str_replace_all(`Index Sequence`, 'tp', ''),
  Sample = paste(`SLX-ID`,sub('-','_',`Index Sequence`),sep='.')
  )
